### 2023-10-29 generalExploration.Rmd
minor edit

            ##repro
            partner=population[[ind]]$partner
            canrepro=population[[ind]]$repro
            if(partner>0 & !canrepro){
                if(logging=="verbose")print(paste("childtest",ind,partner,population[[ind]]$community,population[[partner]]$community))
                population[[partner]]$repro=TRUE #make sure proba of reproduction is unique for all pair 
                ad_tr=initcomus$adaptivetraits[population[[ind]]$community,]
                lambda=b+r*sum(ad_tr)
                nchild=rpois(1,lambda)
                if(nchild>0){
                    for(i in 1:nchild){
                        newborn=reproduction(population[[ind]],population[[partner]],neutraltraitsParam,population[[length(population)]]$id)
                        if(logging=="demo")print(paste("newborn in ",newborn$community))
                        population[[newborn$id]]=newborn
                        initcomus$size[newborn$community]=initcomus$size[newborn$community]+1
                    }
                }
            }
            population[[ind]]$repro=FALSE

@@

    ## Fission
    overloaded=initcomus$size>Th
    if(sum(overloaded)>0){
        for(split in which(overloaded))
            print(paste("community",split,"with size",initcomus$size[split]))
        #        for(split in which(overloaded))

>>>>

            ##repro
            partner=population[[ind]]$partner
            canrepro=population[[ind]]$repro
            if(partner>0 & !canrepro){
                if(logging=="verbose")print(paste("childtest",ind,partner,population[[ind]]$community,population[[partner]]$community))
                population[[partner]]$repro=TRUE #make sure proba of reproduction is unique for all pair

                ad_tr=initcomus$adaptivetraits[population[[ind]]$community,]

                lambda=b+r*sum(ad_tr) #birth rate wrt to community adaptive traits

                nchild=rpois(1,lambda)
                if(nchild>0){
                    for(i in 1:nchild){
                        newborn=reproduction(population[[ind]],population[[partner]],neutraltraitsParam,population[[length(population)]]$id)
                        if(logging=="demo")print(paste("newborn in ",newborn$community))
                        population[[newborn$id]]=newborn
                        initcomus$size[newborn$community]=initcomus$size[newborn$community]+1
                    }
                }
            }
            population[[ind]]$repro=FALSE

@@

    ## Fission
    overloaded=initcomus$size>Th
    if(sum(overloaded)>0){
        listcomu=sapply(population,"[[","community") ##keep list of agent in each commu to avoid that 
        for(split in which(overloaded)){
            print(paste("community",split,"with size",initcomus$size[split]))
            tosplit= (listcomu == split)
            #initcomus
            moving=sample(names(population)[tosplit],initcomus$size[split]/2)
        }
